Title

### 2024-05-13 paper/main.tex
Updates

\section{Introduction}
\textbf{Para 1: Many Causal discovery algorithms but commonly constructed manually.}

\todo[inline]{Add citations}

@@

\textbf{Para 2: Reasons behind this and importance of verifying against data}

@@

\textbf{Para 3: Structural Equation Models, testing, include modification indices}

@@

% modification indices have been used to do this. However, as modification index
% is an evaluation of the global fit of the model. An alternative is local fit of
% models using CI tests where the implied conditional independences of the model
% can be tested using statistical tests. Similar to modification indices, these
% tests can then be used to modify our models. Figure shows an example of this
% testing. We can not also only rely on the p-values, effect size can help in
% deciding.

\textbf{Para 4: Measure of Association}
In the case of DAGs however, we do not have any way to 
As these CI based testing uses p-values and effect size measures from CI tests
for testing. And as mixed data is common, we need both a test and effect size
measure for mixed data. Recently, a few CI tests for mixed data have been
proposed but an effect size is still missing.

\textbf{Para 5: Contributions}
\begin{enumerate}
	\item We present a procedure to construct and modify DAGs using domain
		knowledge.
	\item The presented procedure uses a (conditional) measure of
		association between variables. In the simple case of continuous
		or discrete variables, effect size measures can be used,
		however as no such measure exists for mixed data, we present
		one.
	\item Lastly, to assist researchers in using the DAG construction
		approach, we developed a web-based tool to help researches in
		constructing and modifying their DAGs.
\end{enumerate}

>>>>

\section{Introduction}

@@

@@

@@

In the case of DAGs however, we do not have any way to 
As these CI based testing uses p-values and effect size measures from CI tests
for testing. And as mixed data is common, we need both a test and effect size
measure for mixed data. Recently, a few CI tests for mixed data have been
proposed but an effect size is still missing.

\begin{enumerate}
	\item We present a procedure to construct and modify DAGs using domain
		knowledge.
	\item The presented procedure uses a (conditional) measure of
		association between variables. In the simple case of continuous
		or discrete variables, effect size measures can be used,
		however as no such measure exists for mixed data, we present
		one.
	\item Lastly, to assist researchers in using the DAG construction
		approach, we developed a web-based tool to help researches in
		constructing and modifying their DAGs.
\end{enumerate}
